Testing atlantisom: true biomass output from Atlantis

### 2019-04-29 TrueBioTest.Rmd
add html to docs

```{r matchB, fig.cap="Testing whether the survey census gives the same results as the Atlantis output biomass index file; first 9 species."}
# plot some comparisons with Atlantis output

@@

```{r matchBp3, fig.cap="Testing whether the survey census gives the same results as the Atlantis output biomass index file; last 9 species. Depending on the model, we may not show all species in this example."}
compareB + 
  facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 3, scales="free")

@@

```{r matchBfromN3, fig.cap="Testing whether the survey census based on numbers converted to biomass gives the same results as the Atlantis output biomass index file; last 9 species.Depending on the model, we may not show all species in this example."}

@@

>>>>

```{r matchB, fig.cap="Testing whether the survey census gives the same results as the Atlantis output biomass index file; first 9 species.", message=FALSE, warning=FALSE}
# plot some comparisons with Atlantis output

@@

```{r matchBp3, fig.cap="Testing whether the survey census gives the same results as the Atlantis output biomass index file; next 9 species."}
compareB + 
  facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 3, scales="free")

```{r matchBp4, fig.cap="Testing whether the survey census gives the same results as the Atlantis output biomass index file; last 9 species. Depending on the model, we may not show all species in this example."}
compareB + 
  facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 4, scales="free")

@@

```{r matchBfromN3, fig.cap="Testing whether the survey census based on numbers converted to biomass gives the same results as the Atlantis output biomass index file; next 9 species."}

@@

```{r matchBfromN4, fig.cap="Testing whether the survey census based on numbers converted to biomass gives the same results as the Atlantis output biomass index file; last 9 species.Depending on the model, we may not show all species in this example."}

compareB_N + 
  facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 4, scales="free")
